---
output: github_document
---

<!-- README.md is generated from README.Rmd. Please edit that file -->

```{r, include = FALSE}
knitr::opts_chunk$set(
  collapse = TRUE,
  comment = "#>",
  fig.path = "man/figures/README-",
  out.width = "100%"
)
```

# labradoR

<!-- badges: start -->

[![R-CMD-check](https://github.com/bonifazi/labradoR/actions/workflows/R-CMD-check.yaml/badge.svg)](https://github.com/bonifazi/labradoR/actions/workflows/R-CMD-check.yaml)
`

<!-- badges: end -->

The goal of labradoR is to load and process the output of the Retriever sofware.

labradoR helps you to load the tabular data into data frames for down stream analyses and visualization.

labradoR also generates plots from the data frames.

## Installation

You can install the development version of labradoR from [GitHub](https://github.com/) with:

``` r
# install.packages("devtools")
devtools::install_github("bonifazi/labradoR")
```

## Example usage

This is a basic example showing the package usage:

```{r example, eval=FALSE, include=FALSE}
library(labradoR)
## example usage
output <- process_retriever(file_name = "C:/myPath/pedigree_Retriever.out", language = "ENG")

str(output, max.levels = 1, give.attr = F)
```
