---
title: "Simulation Results Report"
date: "`r Sys.Date()`"
params:
  input_file: C:/Users/bonif002/OneDrive/labradoR_simulation/Retriever/www/upload/sheep_ped.out
  language: ENG
output: github_document
---

```{r setup, include=FALSE}
# Load necessary libraries
library(knitr)
# devtools::install_github("bonifazi/labradoR", quiet = T)
library(labradoR)
options(warn = -1) # suppress warning messages
```

```{r}
packageVersion("labradoR")
```

Example of running labradoR (the `xinterval` and `delta_intervals` arguments are optional arguments).

```{r process retriever file with labradoR}
sim_results <- labradoR::process_retriever(params$input_file, language = params$language, xinterval = c(2006, 2020), delta_intervals = c(2006, 2008, 2010, 2014, 2020))
```

# Description

Report generated from retriever output file using the {labradoR} R package.

Given input file is `r params$input_file`, with `r params$language` as language.

## Population size

```{r}
kable(sim_results$pop_size)
print(sim_results$pop_size_plot)
print(sim_results$sex_ratio_plot)
```

## Sex ratio

```{r}
print(sim_results$sex_ratio_plot)
```

## Inbreeding

```{r}
kable(sim_results$inbreeding)
print(sim_results$inbreeding_plot)
```

## Generation intervals

```{r}
kable(sim_results$gen_intervals)
print(sim_results$gen_intervals_plot)
```

## Mean Age of Fathers

```{r}
kable(sim_results$mean_age_fathers)
print(sim_results$mean_age_fathers_plot)
```

## Mean Age of Mothers

```{r}
kable(sim_results$mean_age_mothers)
print(sim_results$mean_age_mothers_plot)
```

## Pedigree completeness

```{r}
kable(sim_results$pedigree_completeness)
print(sim_results$pedigree_completeness_plot)
```

## Average Generation Equivalent

```{r}
print(sim_results$average_generation_equivalent_plot)
```

## Litter size

```{r}
kable(sim_results$littersize)
print(sim_results$littersize_plot)
```

## Top Sires

```{r}
kable(sim_results$topsires)
print(sim_results$topsires_plot)
```

## Annual and generational rates

F = inbreeding, f = kinship, L = generation interval.

```{r}
kable(sim_results$deltas)
```
